NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-06 paper/Chapters/Chapter2.tex
hypetension tab1 added

Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, past, never smokers), ethnicity (white, non-white), education level, living with a partner or not and other socio-demographic related variables. Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurse.

Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five minute rest. The means of second and third readings, taken at one minute intervals, were used in the current report. Hypertension was defined as a systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.

@@

>>>>

Computer assisted personal interviews were conducted for the selected individuals by trained interviewers to collect background information on smoking habits (current, past, never smokers), ethnicity (white, non-white), education level, living with a partner or not and other socio-demographic related variables. Participants also had their height, weight, blood pressure, waist circumferences (WC) measured by the nurses.

Specifically, blood pressure was measured in a sitting position using an automated, validated machine, the Omron HEM907, after a five minute rest. The means of second and third readings, taken at one minute intervals, were used in the current report. Hypertension was defined as with systolic blood pressure of 140 mmHg or above, and/or diastolic blood pressure of 90 mmHg or above, and/or taking any medication specifically to reduce blood pressure.

@@

Model fitting strategies
